\papertitle

### 2012-10-11 manuscript.tex
Minor edits, update TODOs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}
%TODO ryan

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
%TODO(humphrey)
The flying platform used in this experiment is the H$^2$Bird flapping wing 
MAV. Built around the Silverlit I-Bird RC flyer power train and clap-fling 
wings, the H$^2$Bird has a wingspan of [40?] cm and has a flight weight of 
13 grams. A tail propeller and servo-controlled tail elevator provide 
control in the yaw and pitch axes. The on-board electronics package consists of 
a 40 MIPS microprocessor, 6 DOF IMU, IEEE 802.15.4 radio, VGA camera, and motor 
drivers with a 90 mAh lithium polymer battery. In routine flight, the H$^2$Bird 
averages [1.2 m/s] and can operate for approximately 10 minutes.

%TODO footnote for Silverlit I-Bird
%TODO measure wingspan
%TODO ground speed

@@

\begin{figure}[tb]
\centering
\includegraphics[height=150pt]{figures/h2bird_axes.pdf}
\caption{H$^2$Bird Ornithopter with flight control axes}
\label{fig:h2Bird_axes}
\end{figure}

Attitude estimation and control for the H$^2$Bird runs on-board to achieve 
acceptable tracking performance. We estimate the vehicle pose by naively
integrating the IMU, and use PID for controlling the vehicle. The simplistic 
nature of our approach arises from the stringent resource constraints 
of our platform, but nonetheless is not a completely trivial implementation.

One characteristic of the H$^2$Bird that separates it from other MAVs is the
high pitch angles experienced in routine flight. An Euler angle 
parameterization of the vehicle orientation would suffer from singularities
around these high pitch angles, so we instead represent the vehicle orientation
with quaternions. An additional benefit of the quaternion representation is 
the ability to represent relative body and world coordinate angular displacements 
compactly with quaternion multiplication.%~\cite{bowman:reasoning}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental environment.}
\label{fig:experiment_cartoon}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance}
%TODO cameron

To judge the performance of our system described in the previous sections, we
determined the feasible set of initial conditions that resulted in successful
window traversal. We then conducted experiments to calculate the success rate
both within the feasible region and on the edges of the feasible region. The
following sections detail how we calculated the feasible and infeasible
regions using system identification and present the results of our
experimental trials.

@@

We determined the turning speed and turning radius of the H$^2$Bird
experimentally using the response of the system to the step input of a
clockwise 90 degree turn. The results of this experiment are depicted in
Figure~\ref{fig:step_response}. The data for the experiment was gathered from
the integration of the H$^2$Bird's on-board gyroscope data. We used Matlab to
fit a simple low-order model, $H(s) = \frac{0.94782}{1+0.61998s}$, of the
turning behavior to the step response with the physical heading as the state
and the heading set point as the input. This model serves as a simplification
of both the turning dynamics of the ornithopter and the on-board PID
controller regulating the actuator inputs to reach the desired orientation. We
use this model in Section~\ref{sec:visual_servoing} to determine the backwards
reachable region for navigating through the window in simulation.
\\
The step response has a rise time of approximately 1.4 seconds. The H$^2$Bird
flies at an average forward velocity of 1.2 m/s, so the estimated minimum
turning radius of the robot is 1.07 meters. This flight speed is slower than
the maximum speed of the ornithopter to facilitate more reliable tracking.
\\
%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
\label{sec:visual_servoing}
%TODO cameron

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}
% ryan

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
% humphrey
In order to conduct these experiments on cooperation we designed a new
flapping-wing MAV, known as the H$^2$Bird. Built around the Silverlit I-Bird 
RC flyer power train and clap-fling wings, the H$^2$Bird's wingspan is 26.5 
cm and it has a flight weight of 13 grams. A tail propeller and 
servo-controlled tail elevator provide control in the yaw and pitch axes. The 
on-board electronics package consists of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery. In routine flight, the H$^2$Bird averages 1.2 m/s 
ground speed and can operate for approximately 10 minutes.
%TODO footnote for Silverlit I-Bird
%TODO footnote for ImageProc

@@

\begin{figure}[tb]
\centering
\includegraphics[height=150pt]{figures/h2bird_axes.pdf}
\caption{H$^2$Bird Ornithopter with flight control axes}
\label{fig:h2Bird_axes}
\end{figure}
%TODO label ibird drawing

Attitude estimation and control for the H$^2$Bird runs on-board to achieve 
acceptable tracking performance. We estimate the vehicle pose by naively
integrating the IMU, and use PID for controlling the vehicle.

One characteristic of the H$^2$Bird that separates it from other MAVs is the
high pitch angles achieved in routine flight. An Euler angle 
parametrization of the vehicle orientation suffers from singularities
around these high pitch angles, so we instead represent the vehicle orientation
with quaternions. An additional benefit of the quaternion representation is 
the ability to represent relative body and world coordinate angular displacements 
compactly with quaternion multiplication

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental environment.}
\label{fig:experiment_cartoon}
\end{figure}
%TODO label experiment cartoon

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance}
%TODO cameron
To bound the performance of our system described in the previous sections, we
determined the feasible set of initial conditions that resulted in successful
window traversal. We then conducted experiments to calculate the success rate
both within the feasible region and on the edges of the feasible region. The
following sections detail how we calculated the feasible and infeasible
regions using system identification and present the results of our
experimental trials.

@@

We determined the turning speed and turning radius of the H$^2$Bird
experimentally using the response of the system to the step input of a
clockwise 90 degree turn. We depict the results of this experiment in
Figure~\ref{fig:step_response}. We gathered the data for the experiment by 
integrating the output of H$^2$Bird's on-board gyroscope data. We used MATLAB to
fit a simple low-order model, $H(s) = \frac{0.94782}{1+0.61998s}$, of the
turning behavior to the step response with the physical heading as the state
and the heading set point as the input. This model serves as a simplification
of both the turning dynamics of the ornithopter and the on-board PID
controller regulating the actuator inputs to reach the desired orientation. We
use this model in Section~\ref{sec:visual_servoing} to determine the backwards
reachable region for navigating through the window in simulation.

The step response rise time is approximately 1.4 seconds. The H$^2$Bird
flies at an average forward velocity of 1.2 m/s, so the estimated minimum
turning radius of the robot is 1.07 meters. In experiments, we choose a flight
speed lower thanthe maximum speed of the ornithopter, to facilitate more
robust tracking.
%TODO footnote for MATLAB

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
\label{sec:visual_servoing}
%TODO cameron
